## Projection risk summary {#sec-risk-summary}

@tbl-risk-h1, @tbl-risk-h2-south and @tbl-risk-h2-north summarize the six fishing scenarios from the saved low-productivity projection runs. Spawning biomass (B) and catch are in **thousand tonnes (kt)**. The tables show biomass and the approximate probability of exceeding B~MSY~ at **2, 5 and 10 years after 2026: 2028, 2031 and 2036**, plus catches in 2027–2028. The projections cover 2027–2036 and were recalculated on **11 September 2026**, including ADMB standard errors, with the `jjm.tpl` version identified in the run manifest. Later source revisions are outside this saved result set.

The biomass threshold is the **fixed 2017–2026 mean B~MSY~ from the corresponding base Model 1.06**, consistent with @tbl-status-2026. All three components use steepness 0.65. The single stock and southern component use the 2001–2015 recruitment period; the Far North component retains 1970–2016. Probabilities follow the existing JJM risk-table method, using the projected biomass estimate and its reported ADMB standard error:

$$
P(B_y>B_{\mathrm{MSY}})\;\simeq\;
1-\Phi\left(\frac{B_{\mathrm{MSY}}-\widehat B_y}{\mathrm{SE}(\widehat B_y)}\right).
$$

These are conditional normal approximations with the reference point held fixed. They measure exceedance in each stated year. The probability of remaining above a threshold throughout a period requires a separate calculation, as do the exploratory MCMC summaries.

**Saved TAC scenario.** Scenario 5 retains the 11 September implementation and its realized catches. With the supplied input of **1,674.975 kt**, the saved 2027 catch is **1,491.6 kt** under `h1` and **1,656.65 kt** in total under `h2` (1,489.38 kt southern and 167.27 kt Far North). These catches differ from the input and vary over the projection. This archived scenario therefore describes its recorded catches; use as a projection of a specified annual TAC requires a separately validated run that achieves that TAC in each intended year. The subsequent catch-solver revision is outside the saved results displayed here.

For the **1-stock table, both model runs contribute**: the ten-year extension of `h1_1.06.ls.ctl` supplies projected biomass and its newly calculated ADMB standard error; `h1_1.06.ctl` supplies the base-model B~MSY~ threshold through the original `h1_1.06_1_R.rep`. The precautionary run's own B~MSY~ estimate is separate from the threshold used here. For example, updated scenario 4 in 2028 gives $\widehat B = 5774.30$ kt and $\mathrm{SE}=1147.25$ kt. With the base threshold $6869.029054$ kt, the calculation is $1-\Phi[(6869.029054-5774.30)/1147.25]=0.169986$, displayed as **17%**. Uncertainty in the B~MSY~ threshold is excluded.

**Calculation and run provenance:** global MSY uses `sel_msy` (2011–2025), while scenario 4 both calculates and applies its own `Fmsy_proj` using `sel_fut` (2023–2025), the same future selectivity used in scenarios 1–3. Fitted assessment parameters were held at their saved values; future recruitment deviations were extended with zeros and the Hessian and derived standard errors were recomputed. The original fixed base biomass targets are retained. [Annual risk data](../data/projections/risk-data.csv) and the [run manifest](../data/projections/manifest.json) provide the values, controls, source hash and validation record. Earlier five-year validation files belong to the calculation history; the ten-year records support the tables below.

The supplied 2022 Annex K proposal (@sec-annex-k-guidance) also uses a dynamic limit, 80% and 100% biomass bands, replacement catch and specified TAC stability constraints. These tables describe fixed-BMSY exceedance under saved scenarios. Limit-breach probability and application of the complete harvest control rule require the additional definitions and calculations described in that section.

```{r}
#| label: build-risk-summary
#| include: false
source(file.path(report_dir, "..", "R", "risk_data.R"), local = TRUE)
source(file.path(report_dir, "..", "R", "risk_tables.R"), local = TRUE)
```

```{r}
#| label: tbl-risk-h1
#| tbl-cap: !expr paste0("Single-stock risk summary, h1_1.06.ls. B and catch are in kt; P(B > BMSY) is the approximate annual probability that B exceeds fixed BMSY = ", round(unique(filter(risk_data, Hypothesis == "h1")$BMSY_kt)), " kt. Probabilities are rounded to whole percentages; values below 1% or above 99% are shown as <1 or >99.")
risk_table("h1", 1)
```

```{r}
#| label: tbl-risk-h2-south
#| tbl-cap: !expr paste0("Southern-component risk summary, h2_1.06.ls. B and catch are in kt; P(B > BMSY) is the approximate annual probability that B exceeds fixed BMSY = ", round(unique(filter(risk_data, Hypothesis == "h2", Stock == 1)$BMSY_kt)), " kt. Probabilities are rounded to whole percentages; values below 1% or above 99% are shown as <1 or >99.")
risk_table("h2", 1)
```

```{r}
#| label: tbl-risk-h2-north
#| tbl-cap: !expr paste0("Far North-component risk summary, h2_1.06.ls. B and catch are in kt; P(B > BMSY) is the approximate annual probability that B exceeds fixed BMSY = ", round(unique(filter(risk_data, Hypothesis == "h2", Stock == 2)$BMSY_kt)), " kt. Probabilities are rounded to whole percentages; values below 1% or above 99% are shown as <1 or >99.")
risk_table("h2", 2)
```
